Evolutionary Learning of Policies for MCTS Simulations

### 2012-05-31 presentation/presentation.tex
Fixed type on tree search slide relating to Six and MoHex.
Fixed some typos

\begin{frame}{The Game of Hex - Example Game}
	\begin{figure}[tb]
	\resizebox{3.3in}{!}{ \begin{HexBoard}[board size=7]
		  \HGame{d4,d3,e3,f1,c2,d6}
		\end{HexBoard}
		}
	\end{figure}
	\begin{itemize}
		\item Connect opposing sides
		\item Cut opponents connections
	\end{itemize}
\end{frame}

@@

\begin{frame}{Tree Search}
\begin{itemize}
	\item Game tree grows exponentially
	\begin{itemize}
		\item Hex on a general board is PSPACE-complete
	\end{itemize}
	\item No effective position evaluation heuristic
	\begin{itemize}
		\item Previous champion until 2006, (\emph{Six}, used circuit simulation
	\end{itemize}
	\item Limited opportunities for provable pruning
	\begin{itemize}
		\item Current champion, \emph{MoHex}, does lots of this
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Monte Carlo Tree Search - Playout Policies}
\begin{itemize}
	\item Playout policy a critical part of overall performance
	\item We examine 4 different policies:
	\begin{itemize}
		\item Default - uniform random
		\item Uniform Local - play in local neighborhood first
		\item Uniform Local with Tekuki (Play-Away) - possibly play in local neighborhood first
		\item Local Pattern Weighted - stochastic, weighted local neighborhood
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Results of learning after training on 7x7)}
\begin{figure}
	\caption{Trained on 7x7 board}
	\begin{center}
		\begin{tabular}{c | c c c}
		& \multispan{3}{\hfil opponent \hfil} \\
		 player & default & uniform local & uniform local (tenuki) \\
		\hline
		uniform local & 70.50\% & & \\
		uniform local (tenuki) & 61.00\% & 50.00\% & \\
		learned & \hilight{90.00\%} & \hilight{84.00\%} & \hilight{86.00\%} \\
		\end{tabular}
	\label{fig:results}
	\end{center}
\end{figure}
\begin{itemize}
	\item All-play-all tournament of the 4 policy variants.
	\item Each element is the percent win-rate of the row variant versus the column variant.
	\item 200 games per pair.
\end{itemize}
\end{frame}

>>>>

@@

\begin{frame}{Tree Search}
\begin{itemize}
	\item Game tree grows exponentially
	\begin{itemize}
		\item Hex on a general board is PSPACE-complete
	\end{itemize}
	\item No effective position evaluation heuristic
	\begin{itemize}
		\item \emph{Six}, previous champion until 2006, used circuit simulation
	\end{itemize}
	\item Limited opportunities for provable pruning
	\begin{itemize}
		\item \emph{MoHex}, current champion, does lots of this
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Monte Carlo Tree Search - Playout Policies}
\begin{itemize}
	\item Playout policy a critical part of overall performance
	\item We examine 4 different policies:
	\begin{itemize}
		\item Default - uniform random
		\item Uniform Local - play in local neighborhood first
		\item Uniform Local with Tenuki (Play-Away) - possibly play in local neighborhood first
		\item Local Pattern Weighted - stochastic, weighted local neighborhood
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Results of learning after training on 7x7}
\begin{figure}
	\caption{Trained on 7x7 board}
	\begin{center}
		\begin{tabular}{c | c c c}
		& \multispan{3}{\hfil opponent \hfil} \\
		 player & default & uniform local & uniform local (tenuki) \\
		\hline
		uniform local & 70.50\% & & \\
		uniform local (tenuki) & 61.00\% & 50.00\% & \\
		learned & \hilight{90.00\%} & \hilight{84.00\%} & \hilight{86.00\%} \\
		\end{tabular}
	\label{fig:results}
	\end{center}
\end{figure}
\begin{itemize}
	\item All-play-all tournament of the 4 policy variants.
	\item Each element is the percent win-rate of the row variant versus the column variant.
	\item 200 games per pair.
\end{itemize}
\end{frame}
